---
title: "Data Visualization Intro"
author: Austin Delany
date: '2023-05-11'
output: html_document
---

# Creating Visuals With R Functions

## FlareVis GitHub Repository 
Repo for FLARE visualizations can be found at https://github.com/FLARE-forecast/flareVis

## Forking the branch and cloning locally 

- Go to https://github.com/FLARE-forecast/flareVis and fork the repository (create a copy on your github account)
- Click the green "code" button and copy the HTTPS link 
- Go to your local Rstudio and create a new project (Version Control, Git, URL)

## Create A Visualization 

#read data

```{r}
example_plot <- function(data, depths, tzone, ylims){
  
      p <- ggplot(data, aes(x=datetime,y=prediction, group = parameter)) +
      geom_line() +
      ylab('Temperature (deg C)') +
      xlab('Date')
      ggtitle('FLARE Forecast Members') +
      ylim(ylims) +  
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5))
      
      return(p)
}
```


Read in forecast data -- try to do as much filtering as possible before the collect() statement 

```{r, echo=FALSE}
forecast_s3 <- arrow::s3_bucket('forecasts/parquet', endpoint_override = 's3.flare-forecast.org', anonymous = TRUE)

sunp_data <- arrow::open_dataset(forecast_s3) |>
  dplyr::filter(site_id == 'sunp',
                reference_datetime ==  '2023-05-01 00:00:00',
                variable == 'temperature',
                depth == 1.0) |>
  collect()
```

Call function with data and display plot

```{r}
forecast_fig <- example_plot(sunp_data, depths = NULL, tzone = NULL, ylims = c(0,30))

forecast_fig
```
